### 2021-03-05 text/draft.tex
metrics general

Combining these parameters, we really have 100 Annif configurations
whose performance we want to compare and assess: Annif project \(*\)
text base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).

@@

@@

\begin{itemize}
\tightlist
\item
  best config for department
\end{itemize}

>>>>

Combining these parameters, we really have 100 Annif configurations
whose performance we want to compare and assess: Annif project \(*\)
text base \(*\) maximum number of suggestions \(= 5 * 2 * 10 = 100\).
Each configuration has a unique ID (called ``marker'' in what follows)
constructed by the convention:
\texttt{\{project\_id\}-\{abstract\}-\{fulltext\}-\{n\}-\{threshold\}}
where \texttt{project\_id} is the Annif project, \texttt{abstract} and
\texttt{fulltext} are boolean variables, \texttt{n} is the maximum
number of suggestions per item, and \texttt{threshold} is a variable for
a threshold Annif score.

@@

\begin{figure}
\centering
\includegraphics{images/metrics_f1_top20.pdf}
\caption{Top 20 Annif configurations by F1-score.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/metrics_all_n.pdf}
\caption{Distribution of weighted F1-scores per maximum number of
suggestions 0 \textless{} n \textless11.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/metrics_all_project+abstract.pdf}
\caption{Distribution of weighted F1-scores per class of algorithm
(left) and per class of text basis (right).}
\end{figure}

@@

Let us now look at the results. For each department, we are interested
in the highest weighted F1-score and the corresponding configuration as
summarized in Figure X.

\begin{figure}
\centering
\includegraphics{images/metrics_dept_summary.pdf}
\caption{Best performing Annif configuration by F1-score weighted per
department.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/metrics_dept_distribution.pdf}
\caption{Distribution of F1-scores weighted for all Annif configurations
per department.}
\end{figure}
